More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-11-08 2016-Weak-FH-Bisim/WeakBisim.tex
Skype push

Now focus on OTs of the subnets. For each $m\in I_1\uplus I_2$ we have one of the two 
following OT\footnotemark[\thefootnote]:\\[-2ex]
\[
\pNet_m \models\openrule
    	{
    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}}\]
Or
\[{ \pNet_m 
    	 \models
    	\openrule
    	{\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {\alpha_m}
    		\ostate{s_m'}}}\]

Only elements of $I$ are useful to assert the premise for reduction of $P$; the last 
one ensures the open transition for the pNet $Q$ (note that $Q$ is at place $j_0$, and by 
definition of the open transition 
for $P[Q]_{j_0}$, $I'_{j_0}=I\cap L_Q$, 
$L_{j_0}=L_Q$, and $J_{j_0}=	J\cap\Holes(Q)$):\\[-2ex]
	\[Q\models{\openrule
		{
			\beta_j^{j\in J\cap\Holes(Q)}, \Pred_{j_0},  
			\Post\,''}
		{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_{j_0}}
			\ostate{(s_i')^{\, i\in L_Q}}}
	}\]

@@

\subsection{Composition properties}
\TODO{Ludo: in the next 2 theorems I have a doubt about the biguplus of post p : not sure they should be disjoint, but else we need to do a complex composition  of posts}
\begin{lemma}[Weak OT decomposition]\label{lem-decompose} 
	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
	lemma imply that $Q$ is 
	not a \pLTS\ but a similar lemma can be proven for a pLTS $Q$}:
	\[ P[Q]_{j_0}  
		\models
		{\openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\, i\in L}}}
		}
	\]
		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.
		 Then there exist $v_Q$, $\Pred\,'$,  
		$\Post\,'$,   $\gamma_{j_0}=[\beta_0..\beta_n]$, and for all $p\in[0..n]$ there exist $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and for all $p\in[0..n+1]$ $s_{p i}^{\,i\in L_Q}$. s.t.:\\[-2ex]
		%\[
		\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J_p\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
		}%\]
	\vspace{-2.2ex}\\\text{and for all $p\in[0..n]$~~}
		%\[
		Q\models{\openrule
			{
				\gamma_{p j}^{j\in J_p}, \Pred_p,  
				\Post_p}
			{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
				\ostate{s_{(p+1) i}^{\,i\in L_Q}}}
		}%\]
\\
		\text{and~~}  \bigcup_{\begin{array}{l}
p\in[0..n]
\end{array}} J_{p} = J\cap\Holes(Q) \qquad
 \text{and\qquad} \forall j\in J_p,\,\gamma_j= \mybigdotcup_{p=0}^n \gamma_{p j} \\
 \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\{\hspace{-3ex}}\text{and~~} \Pred \iff \Pred\,'
		\land \!\!\bigwedge_{p=0}^n(\alpha_p=\beta_p\land \Pred_p) \qquad\text{and~}
\Post=\Post\,'\uplus\!\! \biguplus_{p=0}^n
		\Post_p  
		\end{mathpar}
where $\Post_p$ only act upon variables of 
		$\Leaves(Q)$.
\end{lemma}
\LUDO{A V2 by Ludo}
\begin{lemma}[WOT decomposition]\label{lem-wot-decompose} 
	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
	lemma imply that $Q$ is 
	not a \pLTS\ but a similar lemma can be proven for a pLTS $Q$}:
	\[ P[Q]_{j_0}  
		\models
		{\openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\, i\in L}}}
		}
	\]
		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction\footnote{Note that necessarily $\alpha_Q\neq \tau$ as soon as silent actions are not observable Definition~\ref{def:Non-ObsTau}.}.
		 Then there exist $\alpha_Q$, $\Pred\,'$, $\Pred\,''$, 
		$\Post\,'$, $\Post\,''$ s.t.:\\[-2ex]
		%\[
		\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
		}%\]
	\vspace{-2.2ex}\\\text{and~~}
		%\[
		Q\models{\openrule
			{
				\gamma_j^{j\in J\cap\Holes(Q)}, \Pred\,'',  
				\Post\,''}
			{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_Q}
				\ostate{s_i'^{\,i\in L_Q}}}
		}%\]
		\end{mathpar}
		and  $\Pred \iff \Pred\,'
		\land \Pred\,''\land \gamma_{j_0}=[\alpha_Q]$, $\Post=\Post\,'\uplus 
		\Post\,''$ where $\Post\,''$ is the restriction of $\Post$ over variables of 
		$\Leaves(Q)$.

>>>>

Now focus on OTs of the subnets. For each $m\in I_1\uplus I_2$ we have one of the two 
following OT\footnotemark[\thefootnote]:\\
for $m$ in $I_1$
\[
\pNet_m \models\openrule
    	{
    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}}\]
Or, $m$ in $I_2$
\[{ \pNet_m 
    	 \models
    	\openrule
    	{\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {\alpha_m}
    		\ostate{s_m'}}}\]

Only elements of $I_1\backslash\{j_0\}$ and  are useful to assert the premise for reduction of $P$; the last 
one ensures the open transition for the pNet $Q$ (note that $Q$ is at place $j_0$, and by 
definition of the open transition 
for $P[Q]_{j_0}$, $I'_{j_0}=I\cap L_Q$, 
$L_{j_0}=L_Q$, and $J_{j_0}=	J\cap\Holes(Q)$):\\[-2ex]
	\[Q\models{\openrule
		{
			\beta_j^{j\in J\cap\Holes(Q)}, \Pred_{j_0},  
			\Post\,''}
		{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_{j_0}}
			\ostate{(s_i')^{\, i\in L_Q}}}
	}\]

@@

\subsection{Composition properties}
\TODO{Ludo: in the next 2 theorems I have a doubt about the biguplus of post p : not sure they should be disjoint, but else we need to do a complex composition  of posts}
\begin{lemma}[Weak OT decomposition]\label{lem-decompose} 
	Let $\Leaves(Q)=pLTS_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
	lemma imply that $Q$ is 
	not a \pLTS\ but a similar lemma can be proven for a pLTS $Q$}:
	\[ P[Q]_{j_0}  
		\models
		{\openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\, i\in L}}}
		}
	\]
		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.
		 Then there exist $\Pred\,'$,  
		$\Post\,'$,   $\gamma_{j_0}=[\beta_0..\beta_n]$, and for all $p\in[0..n]$ there exist $\alpha_p$, $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and for all $p\in[0..n+1]$ $s_{p i}^{\,i\in L_Q}$. s.t.:\\[-2ex]
		%\[
		\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J_p\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
		}%\]
	\vspace{-2.2ex}\\\text{and for all $p\in[0..n]$~~}
		%\[
		Q\models{\openrule
			{
				\gamma_{p j}^{j\in J_p}, \Pred_p,  
				\Post_p}
			{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
				\ostate{s_{(p+1) i}^{\,i\in L_Q}}}
		}%\]
\\
		\text{and~~}  \bigcup_{\begin{array}{l}
p\in[0..n]
\end{array}} J_{p} = J\cap\Holes(Q) \qquad
 \text{and\qquad} \forall j\in J_p,\,\gamma_j= \mybigdotcup_{p=0}^n \gamma_{p j} \\
 \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\{\hspace{-3ex}}\text{and~~} \Pred \iff \Pred\,'
		\land \!\!\bigwedge_{p=0}^n(\alpha_p=\beta_p\land \Pred_p) \qquad\text{and~}
\Post=\Post\,'\uplus\!\! \biguplus_{p=0}^n
		\Post_p  
		\end{mathpar}
where $\Post_p$ only act upon variables of 
		$\Leaves(Q)$.
\end{lemma}
\LUDO{A V2 by Ludo}
\begin{lemma}[WOT decomposition]\label{lem-wot-decompose} 
	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
	lemma imply that $Q$ is 
	not a \pLTS\ but a similar lemma can be proven for a pLTS $Q$}:
	\[ P[Q]_{j_0}  
		\models
		{\openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\, i\in L}}}
		}
	\]
		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction\footnote{Note that necessarily $\alpha_Q\neq \tau$ as soon as silent actions are not observable Definition~\ref{def:Non-ObsTau}.}.
		 Then there exist $\alpha_Q$, $\Pred\,'$, $\Pred\,''$, 
		$\Post\,'$, $\Post\,''$ s.t.:\\[-2ex]
		%\[
		\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
		}%\]
	\vspace{-2.2ex}\\\text{and~~}
		%\[
		Q\models{\openrule
			{
				\gamma_j^{j\in J\cap\Holes(Q)}, \Pred\,'',  
				\Post\,''}
			{\ostate{s_i^{i\in L_Q}} \OTWeakarrow {\alpha_Q}
				\ostate{s_i'^{\,i\in L_Q}}}
		}%\]
		\end{mathpar}
		and  $\Pred \iff \Pred\,'
		\land \Pred\,''\land \gamma_{j_0}=[\alpha_Q]$, $\Post=\Post\,'\uplus 
		\Post\,''$ where $\Post\,''$ is the restriction of $\Post$ over variables of 
		$\Leaves(Q)$.
